RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2022-12-18 jsac_221218.tex
:triangular_flag_on_post: JSAC and arXiv 221218

\usepackage[table]{xcolor}
\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage{booktabs}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage{ragged2e}
\usepackage[subtle]{savetrees}
\usepackage{setspace}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{tikz}

@@

% algpseudocode
\makeatletter
\renewcommand{\fnum@algorithm}{\fname@algorithm{} \thealgorithm:}
\makeatother
\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
\algrenewcommand{\algorithmicensure}{\textbf{Output:}}
\algrenewcommand{\algorithmicwhile}{\textbf{While}}
\algrenewcommand{\algorithmicend}{\textbf{End}}
\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
\algrenewcommand{\algorithmicuntil}{\textbf{Until}}
\algrenewcommand{\algorithmicdo}{}

@@

\begin{abstract}
	% \gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
	% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
	\gls{ris} adapts its phase shift response to enhance or attenuate channel strength in specific directions.
	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
	RIScatter consists of multiple dispersed or co-located scatter nodes, whose reflection states can be adapted to partially engineer the wireless channel of the existing link and partially modulate their own information onto the scattered wave.
	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
	The key principle in RIScatter is to render the probability distribution of reflection states (i.e., backscatter channel input) as a joint function of the information source, \gls{csi}, and \gls{qos} of the coexisting active primary and passive backscatter links.
	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming, and the proposed practical receiver accommodates the double fading, double modulation, and symbol period difference of active-passive coexisting networks without \gls{sic}.
\end{abstract}

@@

\begin{section}{Introduction}
	% \begin{subsection}{Fundamentals}
	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
	As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
	In particular, the node harvests energy from impinging wave and embeds information over scattered signal, and the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} in Fig.~\subref*{fg:mbc} and \gls{bbc} in Fig.~\subref*{fg:bbc}.
	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
	However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
	To tackle this, \cite{Liu2013b} proposed \gls{ambc} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
	As shown in Fig.~\subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum for \gls{bc}, but the decoding is subject to a strong interference from the primary (legacy) link.
	Cooperative \gls{ambc} was then proposed where a co-located receiver decodes both active primary and passive backscatter links, and the rate and error performance are evaluated for various detection schemes \cite{Yang2018}.
	The concept was further refined by \cite{Liang2020} as \gls{sr} in Fig.~\subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems.
	In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly, individually, or sequentially decodes both links.
	Those \gls{bc} applications employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
	On the other hand, \gls{ris} in Fig.~\ref{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and adaptively optimized based on \gls{csi}.
	\gls{ris} smartly reflects the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
	In summary, \gls{mbc}/\gls{bbc} (resp. \gls{ris}) involves a \emph{single} passive backscatter (resp. active primary) link where the passive device modulates information (resp. enhances propagation) and the active device generates carrier wave (resp. modulated signal).
	On the other hand, \gls{ambc} (resp. \gls{sr}) involves \emph{coexisting} active primary and passive backscatter links in a competitive (resp. collaborative) relationship.
	In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency) of the primary link, while the primary link may be completely unaware of the backscatter link.
	In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
	A comparison of scattering applications is summarized in Table~\ref{tb:scattering_applications}.

@@

	Due to double modulation, the primary equivalent channel is a function of backscatter symbol tuple
		\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k = \boldsymbol{h}_{\text{D}}^\mathsf{H} + \boldsymbol{x}^\mathsf{H} \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\text{C}},

@@

@@

		\begin{algorithm}[!t]
			\caption{Numerical \gls{kkt} Input Distribution Evaluation by Limits of Sequence}
			\label{al:input_distribution}
			\begin{algorithmic}[1]
				\Require $K$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
				\State Set $\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
				\State \phantom{Set} $f(z|\mathcal{H}_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
				\State \phantom{Set} $P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dmtmac}
				\State Initialize $r \gets 0$
				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
				\State Get $P_{\mathcal{K}}^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution} \label{st:input_distribution_begin}
				\State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
				\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information} \label{st:input_distribution_end}
				\Repeat
					\State Update $r \gets r+1$
					\State \phantom{Update} $\boldsymbol{p}_k^{(r)}$, $\forall k$ by \eqref{eq:input_kkt_solution}
					\State Redo step \ref{st:input_distribution_begin}--\ref{st:input_distribution_end}
				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \epsilon$
			\end{algorithmic}
		\end{algorithm}
	\end{subsection}

@@

		where $g_{m_{\mathcal{K}}}(t_{l-1},t_l) \triangleq g_{m_{\mathcal{K}}}(t_l)-g_{m_{\mathcal{K}}}(t_{l-1})$ and
			g_{m_{\mathcal{K}}}(t_l) = t_l\exp\Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\Bigl(-1+\sum_{n=1}^{N-1} \frac{\bigl(n - \frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr) \bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^{n-1}}{n!}\Bigr).
			\label{eq:regularized_incomplete_gamma_gradient_component}

@@

			 & =\sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)                                                                                                                                                                                                                \\

@@

		\begin{algorithm}[!t]
			\caption{Iterative Active Beamforming Optimization by \gls{pgd} with \gls{bls}}
			\label{al:active_beamforming}
			\begin{algorithmic}[1]
				\Require $Q$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\epsilon$
				\Ensure $\boldsymbol{w}^\star$
				\State Set $\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
				\State \phantom{Set} $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
				\State Initialize $r \gets 0$
				\State \phantom{Initialize} $\boldsymbol{w}^{(0)}$, $\lVert\boldsymbol{w}^{(0)}\rVert^2 \le P$
				\State Get $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance} \label{st:gradient_descent_begin}
				\State \phantom{Get} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma}
				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:gradient_descent_end}
				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma_gradient} \label{st:gradient_update_start}
				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_gradient} \label{st:gradient_update_end}
				\Repeat
					\State Update $r \gets r+1$
					\State \phantom{Update} $\gamma^{(r)}\gets\gamma$
					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)} \gets \boldsymbol{w}^{(r-1)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r-1)}(x_{\mathcal{K}})$ \label{st:backtracking_line_search_begin}
					\State \phantom{Update} $\boldsymbol{w}^{(r)}$ by \eqref{eq:beamforming_projection}
					\State Redo step \ref{st:gradient_descent_begin}--\ref{st:gradient_descent_end} \label{st:backtracking_line_search_end}
					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}
						\State Set $\gamma^{(r)}\gets\beta\gamma^{(r)}$
						\State Redo step \ref{st:backtracking_line_search_begin}--\ref{st:backtracking_line_search_end}
					\EndWhile
					\State Redo step \ref{st:gradient_update_start}, \ref{st:gradient_update_end}
				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \epsilon$
			\end{algorithmic}
		\end{algorithm}

@@

		Let $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(x_{m_q})$ and $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) = P_k'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(x_{m_q})$ be two probability distributions with potentially different marginal for tag $k$ at state $m_k$, and define an intermediate function $J \bigl( P_{\mathcal{K}}(x_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) \bigr)$ as

@@

			\Biggl( \rho \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr)                                                                                                                                                    \\

@@

		where $i_k \ne m_k$ is the reference state and

>>>>

\usepackage[table]{xcolor}
\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage{booktabs}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage{ragged2e}
\usepackage[subtle]{savetrees}
\usepackage{setspace}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{tikz}

% page limit hacks
% \usepackage[top=1cm, bottom=1cm, left=1cm, right=1cm]{geometry}
\abovedisplayskip=1mm
\belowdisplayskip=1mm
\abovedisplayshortskip=1mm
\belowdisplayshortskip=1mm
\setlength{\jot}{0.1mm}
\setlength{\floatsep}{1mm}
\setlength{\textfloatsep}{1mm}
\setlength{\intextsep}{1mm}
\setlength{\skip\footins}{1mm}
\theoremstyle{remark}

@@

% algpseudocode
\makeatletter
\renewcommand{\fnum@algorithm}{\fname@algorithm{} \thealgorithm:}
\newcommand\setalgorithmcaptionfont[1]{%
	\let\my@floatc@ruled\floatc@ruled          % save \floatc@ruled
	\def\floatc@ruled{%
		\global\let\floatc@ruled\my@floatc@ruled % restore \floatc@ruled
		#1\floatc@ruled}}
\makeatother

\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
\algrenewcommand{\algorithmicensure}{\textbf{Output:}}
\algrenewcommand{\algorithmicwhile}{\textbf{While}}
\algrenewcommand{\algorithmicend}{\textbf{End}}
\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
\algrenewcommand{\algorithmicuntil}{\textbf{Until}}
\algrenewcommand{\algorithmicdo}{}

@@

\begin{abstract}
	% \gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
	% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
	\gls{ris} adapts its phase shift response to enhance or attenuate channel strength in specific directions.
	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
	RIScatter consists of multiple dispersed or co-located scatter nodes, whose reflection states can be adapted to partially engineer the wireless channel of the existing link and partially modulate their own information onto the scattered wave.
	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
	The key principle in RIScatter is to render the probability distribution of reflection states (i.e., backscatter channel input) as a joint function of the information source, \gls{csi}, and \gls{qos} of the coexisting active primary and passive backscatter links.
	This enables RIScatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming, and the proposed practical receiver accommodates the double fading, double modulation, and symbol period difference of active-passive coexisting networks without \gls{sic}.
\end{abstract}

\begin{IEEEkeywords}
	Backscatter communication, reconfigurable intelligent surface, ambient backscatter communication, symbiotic radio.
\end{IEEEkeywords}

@@

\begin{section}{Introduction}
	% \begin{subsection}{Fundamentals}
	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
	As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
	In particular, the node harvests energy from impinging wave and embeds information over scattered signal, and the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} in Fig.~\subref*{fg:mbc} and \gls{bbc} in Fig.~\subref*{fg:bbc}.
	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
	However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
	To tackle this, \cite{Liu2013b} proposed \gls{ambc} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
	As shown in Fig.~\subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum for \gls{bc}, but the decoding is subject to a strong interference from the primary (legacy) link.
	Cooperative \gls{ambc} was then proposed where a co-located receiver decodes both active primary and passive backscatter links, and the rate and error performance are evaluated for various detection schemes \cite{Yang2018}.
	The concept was further refined by \cite{Liang2020} as \gls{sr} in Fig.~\subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems.
	In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly, individually, or sequentially decodes both links.
	Those \gls{bc} applications employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
	On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and adaptively optimized based on \gls{csi}.
	\gls{ris} smartly reflects the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
	In summary, \gls{mbc}/\gls{bbc} (resp. \gls{ris}) involves a \emph{single} passive backscatter (resp. active primary) link where the passive device modulates information (resp. enhances propagation) and the active device generates carrier wave (resp. modulated signal).
	On the other hand, \gls{ambc} (resp. \gls{sr}) involves \emph{coexisting} active primary and passive backscatter links in a competitive (resp. collaborative) relationship.
	In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency) of the primary link, while the primary link may be completely unaware of the backscatter link.
	In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
	A comparison of scattering applications is summarized in Table~\ref{tb:scattering_applications}.

@@

	Due to double modulation, the primary equivalent channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literatures, respectively.}

@@

			\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{\mathcal{K}})
			 & \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \label{eq:equivalent_channel_bc}                    \\
			 & = \boldsymbol{h}_{\text{D}}^\mathsf{H} + \boldsymbol{x}^\mathsf{H} \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\text{C}}, \label{eq:equivalent_channel_ris}

@@

		\setalgorithmcaptionfont{\small}
		\begin{algorithm}[!t]
			\small
			\caption{Numerical \gls{kkt} Input Distribution Evaluation by Limits of Sequence}
			\label{al:input_distribution}
			\begin{algorithmic}[1]
				\Require $K$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
				\State Set $\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
				\State \phantom{Set} $f(z|\mathcal{H}_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
				\State \phantom{Set} $P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dmtmac}
				\State Initialize $r \gets 0$
				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
				\State Get $P_{\mathcal{K}}^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution} \label{st:input_distribution_begin}
				\State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
				\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information} \label{st:input_distribution_end}
				\Repeat
					\State Update $r \gets r+1$
					\State \phantom{Update} $\boldsymbol{p}_k^{(r)}$, $\forall k$ by \eqref{eq:input_kkt_solution}
					\State Redo step \ref{st:input_distribution_begin}--\ref{st:input_distribution_end}
				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \epsilon$
			\end{algorithmic}
		\end{algorithm}
	\end{subsection}

@@

		where $g_{m_{\mathcal{K}}}(t_{l-1},t_l) \triangleq g_{m_{\mathcal{K}}}(t_l)-g_{m_{\mathcal{K}}}(t_{l-1})$ and $g_{m_{\mathcal{K}}}(t_l) = t_l\exp\Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\Bigl(-1+\sum_{n=1}^{N-1} \frac{\bigl(n - \frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr) \bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^{n-1}}{n!}\Bigr)$.
		% \begin{equation}
		% 	g_{m_{\mathcal{K}}}(t_l) = t_l\exp\Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\Bigl(-1+\sum_{n=1}^{N-1} \frac{\bigl(n - \frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr) \bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^{n-1}}{n!}\Bigr).
		% 	\label{eq:regularized_incomplete_gamma_gradient_component}
		% \end{equation}

@@

			 & =\sum_{m_{\mathcal{K}}}P_{\mathcal{K}}(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr) \nonumber                                                                                                                                                                                                      \\

@@

		\setalgorithmcaptionfont{\small}
		\begin{algorithm}[!t]
			\small
			\caption{Iterative Active Beamforming Optimization by \gls{pgd} with \gls{bls}}
			\label{al:active_beamforming}
			\begin{algorithmic}[1]
				\Require $Q$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\epsilon$
				\Ensure $\boldsymbol{w}^\star$
				\State Set $\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
				\State \phantom{Set} $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
				\State Initialize $r \gets 0$
				\State \phantom{Initialize} $\boldsymbol{w}^{(0)}$, $\lVert\boldsymbol{w}^{(0)}\rVert^2 \le P$
				\State Get $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance} \label{st:gradient_descent_begin}
				\State \phantom{Get} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma}
				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:gradient_descent_end}
				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma_gradient} \label{st:gradient_update_start}
				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_gradient} \label{st:gradient_update_end}
				\Repeat
					\State Update $r \gets r+1$
					\State \phantom{Update} $\gamma^{(r)}\gets\gamma$
					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)} \gets \boldsymbol{w}^{(r-1)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r-1)}(x_{\mathcal{K}})$ \label{st:backtracking_line_search_begin}
					\State \phantom{Update} $\boldsymbol{w}^{(r)}$ by \eqref{eq:beamforming_projection}
					\State Redo step \ref{st:gradient_descent_begin}--\ref{st:gradient_descent_end} \label{st:backtracking_line_search_end}
					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}
						\State Set $\gamma^{(r)}\gets\beta\gamma^{(r)}$
						\State Redo step \ref{st:backtracking_line_search_begin}--\ref{st:backtracking_line_search_end}
					\EndWhile
					\State Redo step \ref{st:gradient_update_start}, \ref{st:gradient_update_end}
				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \epsilon$
			\end{algorithmic}
		\end{algorithm}
	\end{subsection}

@@

		Let $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(x_{m_q})$ and $P_{\mathcal{K}}'(x_{m_{\mathcal{K}}}) = P_k'(x_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(x_{m_q})$ be two probability distributions with potentially different marginal for tag $k$ at state $m_k$, and define an intermediate function

@@

			\Biggl( \rho \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr) \nonumber                                                                                                                                          \\

@@

		where $S_k'(x_{m_k}) \triangleq I_k'(x_{m_k}) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log P_{\mathcal{K}}'(x_{m_{\mathcal{K}}})$ and $i_k \ne m_k$ is the reference state.
